イーサリアム: 安全な分散型汎用トランザクション台帳\\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}

### 2022-07-19 Paper.tex

\begin{abstract}
The blockchain paradigm when coupled with cryptographically-secured transactions has demonstrated its utility through a number of projects, with Bitcoin being one of the most notable ones. Each such project can be seen as a simple application on a decentralised, but singleton, compute resource. We can call this paradigm a transactional singleton machine with shared-state.

Ethereum implements this paradigm in a generalised manner. Furthermore it provides a plurality of such resources, each with a distinct state and operating code but able to interact through a message-passing framework with others. We discuss its design, implementation issues, the opportunities it provides and the future hurdles we envisage.
\end{abstract}

>>>>

\begin{abstract}
    ブロックチェーンパラダイムは、暗号化された安全な取引と結びついたとき、多くのプロジェクトを通じてその有用性を実証しており、ビットコインは最も注目すべきものの1つです。
    このようなプロジェクトは、分散型だがシングルトンの計算資源上の単純なアプリケーションと見なすことができる。
    このパラダイムを、共有された状態(shared-state)を持つトランザクショナル・シングルトン・マシンと呼ぶことができる。

    Ethereumはこのパラダイムを一般化した形で実装しています。さらに、このようなリソースを複数用意し、それぞれが個別の状態と操作コードを持つが、メッセージパッシングのフレームワークを通じて他のリソースと相互作用することが可能である。

    本稿では、イーサリアムの設計、実装上の問題点、提供される機会、そして我々が想定する将来のハードルについて議論する。
\end{abstract}
